Examining background gene lists using simulation - comparison of different enrichment techniques

### 2024-09-12 docker_results/analysis/sim/run_simpw.Rmd
better boxplots with means

@@

par(mfrow=c(1,3))
par(mar=c(c(9.1, 3.5, 2.1, 1.1) ))
boxplot(prec,cex=0,main="precision",ylab="",col="white",las=2)
beeswarm(prec,add=TRUE,col="black",pch=19)
boxplot(rec,cex=0,main="recall",ylab="",col="white",las=2)
beeswarm(rec,add=TRUE,col="black",pch=19)
boxplot(f1,cex=0,main="F1 index",ylab="",col="white",las=2)
beeswarm(f1,add=TRUE,col="black",pch=19)

png("fig3_box.png", width=7,height=5,units="in",res=150,pointsize=12)
par(mar=c(c(9.1, 3.5, 2.1, 1.1) ))
par(mfrow=c(1,3))
boxplot(prec,cex=0,main="precision",ylab="",col="white",las=2)
beeswarm(prec,add=TRUE,col="black",pch=19)
boxplot(rec,cex=0,main="recall",ylab="",col="white",las=2)
beeswarm(rec,add=TRUE,col="black",pch=19)
boxplot(f1,cex=0,main="F1 index",ylab="",col="white",las=2)
beeswarm(f1,add=TRUE,col="black",pch=19)
dev.off()

pdf("fig3_box.pdf", width=7,height=5,pointsize=12)
par(mar=c(c(9.1, 3.5, 2.1, 1.1) ))
par(mfrow=c(1,3))
boxplot(prec,cex=0,main="precision",ylab="",col="white",las=2)
beeswarm(prec,add=TRUE,col="black",pch=19)
boxplot(rec,cex=0,main="recall",ylab="",col="white",las=2)
beeswarm(rec,add=TRUE,col="black",pch=19)
boxplot(f1,cex=0,main="F1 index",ylab="",col="white",las=2)
beeswarm(f1,add=TRUE,col="black",pch=19)
dev.off()

>>>>

if (file.exists("res.Rds"") {

  res <- readRDS("res.Rds")

} else {

@@

par(mfrow=c(1,3))
par(mar=c(c(9.1, 3.5, 2.1, 1.1) ))
boxplot(prec,cex=0,main="precision",ylab="",col="white",las=2)
beeswarm(prec,add=TRUE,col="darkgray",pch=19)
beeswarm(lapply(prec,mean),add=TRUE,col="black",pch="x")
boxplot(rec,cex=0,main="recall",ylab="",col="white",las=2)
beeswarm(rec,add=TRUE,col="darkgray",pch=19)
beeswarm(lapply(rec,mean),add=TRUE,col="black",pch="x")
boxplot(f1,cex=0,main="F1 index",ylab="",col="white",las=2)
beeswarm(f1,add=TRUE,col="darkgray",pch=19)
beeswarm(lapply(prec,f1),add=TRUE,col="black",pch="x")

png("fig3_box.png", width=7,height=5,units="in",res=150,pointsize=12)
par(mar=c(c(9.1, 3.5, 2.1, 1.1) ))
par(mfrow=c(1,3))
boxplot(prec,cex=0,main="precision",ylab="",col="white",las=2)
beeswarm(prec,add=TRUE,col="darkgray",pch=19)
beeswarm(lapply(prec,mean),add=TRUE,col="black",pch="x")
boxplot(rec,cex=0,main="recall",ylab="",col="white",las=2)
beeswarm(rec,add=TRUE,col="darkgray",pch=19)
beeswarm(lapply(rec,mean),add=TRUE,col="black",pch="x")
boxplot(f1,cex=0,main="F1 index",ylab="",col="white",las=2)
beeswarm(f1,add=TRUE,col="darkgray",pch=19)
beeswarm(lapply(prec,f1),add=TRUE,col="black",pch="x")
dev.off()

pdf("fig3_box.pdf", width=7,height=5,pointsize=12)
par(mar=c(c(9.1, 3.5, 2.1, 1.1) ))
par(mfrow=c(1,3))
boxplot(prec,cex=0,main="precision",ylab="",col="white",las=2)
beeswarm(prec,add=TRUE,col="darkgray",pch=19)
beeswarm(lapply(prec,mean),add=TRUE,col="black",pch="x")
boxplot(rec,cex=0,main="recall",ylab="",col="white",las=2)
beeswarm(rec,add=TRUE,col="darkgray",pch=19)
beeswarm(lapply(rec,mean),add=TRUE,col="black",pch="x")
boxplot(f1,cex=0,main="F1 index",ylab="",col="white",las=2)
beeswarm(f1,add=TRUE,col="darkgray",pch=19)
beeswarm(lapply(prec,f1),add=TRUE,col="black",pch="x")
dev.off()
